### 2012-05-11 docs/matching_algo/matching_algo.tex
Add pre- and post-conditions for concrete matching

\documentclass{article}
\usepackage{fullpage}
\usepackage{graphicx}

@@

@@

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fullpage}
\usepackage{graphicx}

\DeclareMathOperator{\dom}{dom}
\DeclareMathOperator{\codom}{cod}

@@

\section{Normalisation}

We normalise both the pattern and target graphs by ensuring that
\begin{itemize}
\item each wire connected to a node-vertex at both ends has exactly two wire-vertices on it
\item boundary vertices are adjacent to either node-vertices or another boundary vertex
\item circles (wires in a loop with no node-vertices) have exactly two wire-vertices on them
\end{itemize}

@@

\subsection{Preconditions}
\begin{itemize}
\item $L$ and $G$ are both normalised
\item $U_c\cap\dom(m) = U_w\cap\dom(m) = U_n\cap\dom(m) = \varnothing$ (ie: the vertices in the unmatched sets are not part of the existing matching)
\item each vertex in $U_w$ is adjacent to something in $U_n\cup P$ (ensures we can always reach wire vertices in $U_w$ by starting from a node-vertex in $U_n$ or $P$)
\item $P \subseteq \dom(m)$ ($P$ contains either partially-matched or completely-matched vertices)
\item $U_c$ genuinely does contain circles
\end{itemize}

\subsection{Postconditions}
These are true for the match state that results from each successful branch:
\begin{itemize}
\item $U_c = U_w = U_n = P = \varnothing$ (we cleaned up after ourselves)
\item $P$ is exactly the set of vertices in $\dom(m)$ that are adjacent to a vertex not in $\dom(m)$ ($P$ contains exactly the partially-matched vertices)
\item $\dom(m)$ is the union of the initial states of $U_c$, $U_w$, $U_n$ and $\dom(m)$ (we have matched everything we were asked to, and not lost anything in the process)
\item $m$ induces a graph monomorphism from the full subgraph of $L$ described by $\dom(m)$ to the full subgraph of $G$ described by $\codom(m)$ ($m$ is actually a partial matching from $L$ to $G$)
\end{itemize}
